On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-01-14 manuscript/manuscript.tex
simulation setting suggestions

@@

@@

Continuing with the simulation study, 
Throughout the simulation we assume a working AR(1) dependence structure
regardless of the true dependence. This is demonstrated with different dependence
structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.

@@

@@

\begin{enumerate}
\item
  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process
  with innovation variance $1 / \sigma^2$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
  the observed data.
\item
  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator
  $\hat\theta_n^*$
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
    distribution of the $B$ test statistics to approximate
    the null distribution of the observed statistic.
\end{enumerate}

>>>>

\jy{Simulation study: let's use two distributions:
  $N(8, 8)$ and $\Gamma(8, 1)$. These two distributions have the same means and
  variances. So we could use them to study powers of the tests too.}

@@

\jy{For the same two marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$, let's
  generate data from dependence structures of AR(1) with two coefficients
  $\psi \in \{ -0. 5, 0.5\}$.}

@@

\jy{Here we work on the same marginal distributions $N(8, 8)$ and $\Gamma(8, 1)$
  with different dependence structures:
  ARMA(1, 1); MA(2); AR(2)
  }
Continuing with the simulation study, 
Throughout the simulation we assume a working AR(1) dependence structure
regardless of the true dependence. This is demonstrated with different dependence
structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.

@@

\jy{need a paragraph to describe the misuse and explain the results. Repeat the
  study at the begining of the last section.}

@@

\begin{enumerate}
\item
  Generate $Z_1^*, \ldots, Z_n^*$ from the fitted ARMA$(p, q)$ process
  with innovation variance $1 / \sigma^2$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
  the observed data.
\item
  Fit $F_\theta$ to the bootstrap sample $X_1^*, \ldots, X_n^*$ and obtain estimator
  $\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of the $B$ test statistics to approximate
  the null distribution of the observed statistic.
\end{enumerate}

\jy{For the simulation study, repeat the study at the end of the last section.}
